SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-04-02 design_impl.tex
Added one more use of "underlying" to describe SPP
Added missing period and other small typo fixes.

This section describes a case study implementation of PPF and the
range of features that are used to determine the usefulness of
prefetches.  Here, we have selected SPP as the base engine prefetcher.

@@

\noindent \textbf{Exporting Features from SPP:} PPF uses the meta-data 
specific to SPP, to build some of the perceptron features. These include
the lookahead depth, signature and the confidence counter. These features 
were made visible to PPF\\
%
\noindent \textbf{Original Thresholds Discarded:} In PPF, the
perceptron sum is used to decide whether to prefetch or not, and the
fill-level in case of prefetch.  Thus, the confidence thresholds used 
by SPP -- T\textsubscript{f} and T\textsubscript{p} are no longer needed to
throttle the prefetcher and can be discarded.
%
%\pg{Note, however, as we discuss later, we
%use these confidence thresholds a feature in PPF so the mechanism is
%retained. -- right?}
% djimenez: keeping comments on every line here so it doesn't screw up my
%"roll-your-own" itemized list. don't put in any newlines.
%
%
% EB: Can this point be removed?
% djimenez: I think this would be necessary to reproduce our results so leave it in. 
% EB: It's ultimately a check to avoid SPP's internal segfault. Won't have a real impact.
%
%\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline The
%  original SPP does not consider the slots available in the L2 MSHR
%  queue.  It has the assumption that at no time can the number of
%  suggested prefetches exceed the capacity of the queue.  While it was
%  not described in the paper, the internal confidence mechanism makes
%  sure that the above assumption was maintained.  In PPF, since there
%  cannot be an assumption on the degree of aggressiveness of the
%  underlying prefetcher, we explicitly check that at no point should
%  the number of suggested prefetches exceed the L2 MSHR queue. \pg{is
%    this a big deal?  Seems like a detail}
%

>>>>

This section describes a case study implementation of PPF and the
range of features that are used to determine the usefulness of
prefetches.  Here, we have selected SPP as the underlying prefetcher.

@@

\noindent \textbf{Exporting Features from SPP:} PPF uses metadata 
specific to SPP to build some of the perceptron features. These include
the lookahead depth, signature, and the confidence counter. These features 
were made visible to PPF.\\
%
\noindent \textbf{Original Thresholds Discarded:} In PPF, the
perceptron sum is used to decide whether to prefetch or not, and the
fill-level in case of prefetch.  Thus, the confidence thresholds used 
by SPP -- T\textsubscript{f} and T\textsubscript{p} are no longer needed to
throttle the prefetcher and can be discarded.
%
%\pg{Note, however, as we discuss later, we
%use these confidence thresholds a feature in PPF so the mechanism is
%retained. -- right?}
% djimenez: keeping comments on every line here so it doesn't screw up my
%"roll-your-own" itemized list. don't put in any newlines.
%
%
% EB: Can this point be removed?
% djimenez: I think this would be necessary to reproduce our results so leave it in. 
% EB: It's ultimately a check to avoid SPP's internal segfault. Won't have a real impact.
%
%\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline The
%  original SPP does not consider the slots available in the L2 MSHR
%  queue.  It has the assumption that at no time can the number of
%  suggested prefetches exceed the capacity of the queue.  While it was
%  not described in the paper, the internal confidence mechanism makes
%  sure that the above assumption was maintained.  In PPF, since there
%  cannot be an assumption on the degree of aggressiveness of the
%  underlying prefetcher, we explicitly check that at no point should
%  the number of suggested prefetches exceed the L2 MSHR queue. \pg{is
%    this a big deal?  Seems like a detail}
%
